### 2020-03-09 README.Rmd
Added fit_bayesain_model to readme and necessary changes to package

>>>>

Now we are ready to fit the competition model with `fit_bayesian_model` this takes two inputs: `focal_vs_comp` the data frame with focal trees connected to their competitors and `model_specs` which specifies the notion of competition.

```{r}
bw_fit_model <- focal_vs_comp_bw %>% fit_bayesian_model(model_specs = bw_specs)
```
